Applied Measure Theory for Probabilistic Modeling

### 2022-05-13 paper/paper.tex
edits

>>>>

Treating likelihoods and pointwise products explicitly in this way gives an easy route to many performance optimizations. For example, the likelihood of a linear model can be computed very efficiently in terms of basic linear algebra, and in cases of conjugacy the pointwise product simplifies to a measure that can be expressed in closed form.
